### 2021-03-16 paper.Rmd
Slice tour paragraphs and figure.

For any method we need to ensure that each projection along the interpolated path is still orthonormal. In the case of one-dimensional projections, the set of bases traces a path along the surface of a hypersphere of radius one, as illustrated in Figure (XXX adding an illustration using ferrn). For higher-dimensional projections this is generalised and we find the path along the surface of a torus instead (need to check about this with Sherry).

@@

Projections can hide certain features, sections can provide additional information @Furnas1994-dz
Sectioning a high-dimensional space in systematic manner is challenging, there are a lot of choices we need to make
Typical approach is interactive: brushing to select sections in one view, highlight points in a second view, e.g. a tour display
Slice tour approach: use distance from the projection plane (through a selected center point), update the section systematically with the projection plane @Laa2020-js
Summary of applications: viewing geometric shapes, model visualization
Connection with projection pursuit: section pursuit @Laa2020-ni

\begin{figure*}
   \centering
         \includegraphics[width=0.9\textwidth]{figures/slice_tour_left.jpg}
         \includegraphics[width=0.9\textwidth]{figures/slice_tour_right.jpg}
\caption{Ursula to write}
\label{fig:tour-slice}
\end{figure*}

>>>>

For any method we need to ensure that each projection along the interpolated path is still orthonormal. In the case of one-dimensional projections, the set of bases traces a path along the surface of a hypersphere of radius one, as illustrated in Figure (XXX adding an illustration using ferrn). For higher-dimensional projections this is generalized and we find the path along the surface of a torus instead (need to check about this with Sherry).

@@

The classic tour displays work with projections, and interactive systems like GGobi also provide the option of adding sectioning information via linked brushing. Sectioning can be considered as providing complementary information, and in combination with projections we can for example gain insights into the dimensionality of a data structure [@Furnas1994-dz]. Sectioning a high-dimensional space in systematic manner (without interactive selection of data sections) is challenging, since there is a lot of freedom in choosing a section. A new approach is implemented in the slice tour display [@Laa2020-js], which is using the distance of each from the current projection plane (typically placed such that it passes through the data mean) to highlight points that are nearby and fade out points further from the plane.

The slice tour can reveal concave or non-linear structures obscured in projections, as well as small structures hidden near the center of a distribution. An example showing snapshots of the slice tour of points distributed on the surface of geometric shapes is shown in Fig. \ref{fig:tour-slice}. As with projections, an index function may be used to select target planes showing interesting slices of the data, and we can define a section pursuit guided tour [@Laa2020-ni].

\begin{figure*}[ht]
\centerline{\includegraphics[width=0.2\textwidth]{figures/roman-surface-centered-010.png}
\hspace{5mm}
\includegraphics[width=0.2\textwidth]{figures/torus-4-centered-015.png}
\hspace{5mm}
\includegraphics[width=0.2\textwidth]{figures/cube-6-centered-001.png}}
\centerline{
\includegraphics[width=0.2\textwidth]{figures/roman-surface-centered-032.png}
\hspace{5mm}
\includegraphics[width=0.2\textwidth]{figures/torus-4-centered-033.png}
\hspace{5mm}
\includegraphics[width=0.2\textwidth]{figures/cube-6-centered-063.png}
}
\caption{Still views of the slice tour display showing geometric shapes: Roman surface (left), 4D torus (middle) and a 6d cube (right).}
\label{fig:tour-slice}
\end{figure*}

<!--
\begin{figure*}
   \centering
         \includegraphics[width=0.9\textwidth]{figures/slice_tour_left.jpg}
         \includegraphics[width=0.9\textwidth]{figures/slice_tour_right.jpg}
\caption{Ursula to write}
\label{fig:tour-slice}
\end{figure*}
-->
